### 2023-03-12 main/chapter_2ljets.tex
write overlap removal procedure

>>>>

This sequential overlap procedure is described as follows:
\begin{enumerate}
\item Remove any electron candidate that shares an inner-detector track with a
baseline muon.
This reduces backgrounds from events with
$\mu\to\mu\gamma$, $\gamma\to e^+ e^-$ radiations in the detector.
\item Remove any baseline jet within $\Delta R \leq 0.2$ of a baseline electron.
\item Remove any electron within
$\Delta R \leq \min(0.04 + (10\,\eV[G]) / p_T^e, 0.4)$
of a baseline jet.
This suppresses backgrounds from heavy-flavour hadron decays.
\item Remove any baseline jet that is within $\Delta R \leq 0.2$ of a baseline
muon, or that shares a track with a muon.
\item Remove any muon within
$\Delta R \leq \min(0.04 + (10\,\eV[G]) / p_T^\mu, 0.4)$
of a baseline jet.
This is matches the electron removal instruction above.
\end{enumerate}
The $\ptmiss$ calculation also ignores any electron that shares a calorimeter
cluster with a photon~\cite{atlas2022searches}.
